%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

% \usepackage{times}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

% \usepackage{mathptmx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape David Benjamin} \\ \vspace{1pt}
    \small 610-955-1904 $|$ \href{mailto:davidnbenjamin15@gmail.com}{\underline{davidnbenjamin15@gmail.com}} $|$ 
    \href{davidbenjamin.dev}{\underline{davidbenjamin.dev}} $|$
    \href{https://www.linkedin.com/in/davidbenj15/}{\underline{linkedin.com/in/davidbenj15}} $|$
    \href{https://github.com/DavidBenj15}{\underline{github.com/DavidBenj15}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Johns Hopkins University}{Baltimore, MD}
      {B.S. in Computer Science $|$ Minor in Entrepreneurship \& Management $|$ GPA: 3.92}{Expected May 2027}
  \resumeSubHeadingListEnd
  % \resumeItemListStart
  %   \resumeItem{Relevant Coursework: Artificial Intelligence, Computing in NumPy, Programming in C/C++ on Linux, Software System Design, Data Structures, Algorithms, Full Stack Development, Computing in Java, Professional Writing and Communication}
  %   % \small{\item{Clubs \& Activities: Pava Accelerator, Software Engineering Club, Phi Gamma Delta Fraternity, Golf, Lacrosse, Lifting, Skiing}}


  % \resumeItemListEnd
    \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
        \item{
            \textbf{Relevant Coursework}: Artificial Intelligence, Data Structures, Algorithms, Software System Design, Full Stack Development, Programming in C/C++ on Linux, Computing in Java, Computing in NumPy, Professional Writing and Communication
        }
    }
\end{itemize}

  %-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{
        \item{
            \textbf{Programming Languages:} Python, JavaScript, TypeScript, Java, C, C++, SQL, Bash \\
            \textbf{Frameworks \& Libraries:} React, Node.js, HTML, CSS, Pandas, NumPy, Next.js \\
            \textbf{Tools \& Platforms:} Linux/UNIX, AWS, Docker, Git, GitHub, Windows, Microsoft Office \\
            \textbf{Methodologies:} Agile (Scrum), CI/CD (GitHub Actions), Testing (Unit, Integration, System, TDD), API Design
        }
    }
\end{itemize}



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart     
      

    \resumeSubheading
      {National Aeronautics and Space Administration (NASA)}{May 2025 -- Present}
      {Software Engineer Intern}{Greenbelt, MD}
      \resumeItemListStart
        \resumeItem{Built a constraint-based reviewer assignment tool with Google OR-Tools (CP-SAT) and Django, cutting space telescope proposal scheduling from 7 days to under 1 hour while meeting 15+ constraints on bias, workload, and compliance.}
        \resumeItem{Eliminated timeout failures by implementing asynchronous processing with Celery and Redis, enabling uninterrupted long-running constraint solver jobs and improving system reliability for users.}
        \resumeItem{Developed a name disambiguation module leveraging RapidFuzz and nickname heuristics, significantly improving conflict detection accuracy to reduce bias during proposal-reviewer assignment.}

      \resumeItemListEnd

\resumeSubheading
    {Meta × Major League Hacking (MLH)}{June 2025 -- Present}
    {Site Reliability Engineering Fellow}{Remote}
    \resumeItemListStart
    \resumeItem{Selected for competitive 12-week fellowship (acceptance rate $<$2.5\%) under the direct mentorship of Meta Production Engineers, applying Software and Site Reliability Engineering practices.}
    \resumeItem{Deployed production-grade portfolio website on Linux (DigitalOcean VPS) with Nginx reverse proxy, Docker containerization, MySQL database, and CI/CD pipelines via GitHub Actions.}
    \resumeItem{Implemented Prometheus/Grafana monitoring stack for real-time metrics, alerting, and incident response; gained proficiency in Linux system administration and TDD practices.}

    \resumeItemListEnd

    \resumeSubheading
      {JHU Sports Analytics Research Group}{May 2024 -- May 2025}
      {Lead Software Engineer}{Baltimore, MD}
      \resumeItemListStart
        \resumeItem{Led a team of 9 to build the Atlantic League of Professional Baseballs’s first league-wide analytics platform, introducing MLB-style advanced analytics access and tool sharing to modernize team operations.}
        \resumeItem{Democratized access to 60,000+ Trackman data points/game by deploying an ETL pipeline (Pandas, AWS Lambda, Docker) and REST API (PostgreSQL, AWS API Gateway); currently used by 10+ developers to build 5+ statistical apps.}
        \resumeItem{Built and deployed a full-stack web app with Next.js, TypeScript, Express.js, and Tailwind CSS to unify the discovery and use of analytics baseball tools; currently serving 100+ users.}
      \resumeItemListEnd
    
      
    \resumeSubheading
      {HopHacks}{December 2024 -- Present}
      {Full Stack Software Engineer, Organizer}{Baltimore, MD}
      \resumeItemListStart
        \resumeItem{Automated deployment for HopHacks website by designing a GitHub Actions CI/CD pipeline, reducing manual EC2 deployment steps by 100\% and eliminating downtime via safe, zero-downtime rsync + build promotion strategy.}
        \resumeItem{Built core full stack features to support 500+ hackers and judges using React, Flask, MongoDB, and Amazon S3. }

      \resumeItemListEnd

  \resumeSubHeadingListEnd



% -----------PROJECTS-----------
    \section{Projects \& Hackathons}
      \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Alibaba Global E-Commerce Challenge (2\textsuperscript{nd} / 500+ Global Teams)}}{}
          \resumeItemListStart
            \resumeItem{Built an AR “View in Your Space” web app using React, Tailwind, and Google's $<$model-viewer$>$ to boost Alibaba sales in developing markets.}

            \resumeItem{Selected as a finalist to pitch live to 70+ Alibaba engineers and executives; earned 2\textsuperscript{nd} place globally out of 500+ teams.}
          \resumeItemListEnd
          
        \resumeProjectHeading
          {\textbf{ColdMap}}{}
          \resumeItemListStart
            % \resumeItem{Built an interactive map-based dashboard in Palantir AIP to visualize upcoming cell therapy shipment risks, showing routes, excursion likelihood, and top contributing factors.}
            %  \resumeItem{Built an ETL and logistic regression pipeline using Polars and scikit-learn for shipment risk prediction. Integrated GPT-4o into the dashboard to surface insights, flag high-risk routes, and auto-draft alert emails in natural language.}
            \resumeItem{Built a Palantir AIP dashboard to visualize cell therapy shipment risks and contributing factors. Developed an ETL + logistic regression pipeline (Polars, scikit-learn) for risk prediction and explainability, integrating GPT-4o to surface insights, flag high-risk routes, and auto-draft alert emails.}

          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{Brody Bot}}{}
          \resumeItemListStart
            \resumeItem{Automated study room reservations for 20+ students at Johns Hopkins with a configurable Python + Selenium script.}
            \resumeItem{Bypassed user booking limits using multiprocessing; coordinated concurrent bots and handled race conditions using SQLite.}
          \resumeItemListEnd

      \resumeSubHeadingListEnd

    \section{Activities}
         \begin{itemize}[leftmargin=0.15in, label={}]
            \small{\item{
             % \textbf{Soft Skills}{: Public speaking, Communication, Active listening, Attention to detail} \\
             {Pava Accelerator, Software Engineering Club, Phi Gamma Delta Fraternity, Golf, Lacrosse, Lifting, Skiing} \\
            }}
         \end{itemize}

\end{document}
